Synthesizing Verified Components~~~\\ for Cyber Assured Systems Engineering~ \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2021-08-01 paper/intro.tex
Slight wordsmithing

In recent years, aerospace stakeholders have realized that avionics systems are subject to possible cyber-attacks just like other cyber-physical systems.  Thus, in addition to being fault-tolerant, safety-critical avionics systems must also be {\em cyber-resilient}. Cyber-resiliency means that the system is tolerant to cyberattacks just as safety-critical systems are tolerant to random faults: they recover and continue to execute their mission function, or safely shut down, as requirements dictate.

@@

Another novel aspect of the approach is the synthesis of the AGREE specifications for the high-assurance components to CakeML, a verified compiler implementation for the functional programming language ML \cite{cakeml}. This paper describes in detail the synthesis path from specifications to CakeML code, providing a formal framework in which to argue correctness. CakeML then provides a verified compilation path to several different target binaries proving that the meaning of the CakeML is exactly preserved in the final binaries. Assuming that the execution schedule of the deployed cyber-hardened system is as intended by the AADL model, and that the HAMR-generated communication fabric delivers messages between components as expected, the AGREE model checking results hold for the deployed system, \ie, it detects and prevents the indicated cyber-vulnerabilities over all possible finite inputs. Work is ongoing to lift this result to infinite input traces as these systems are inherently reactive and intended to run forever~\cite{case-verified-filter}, \cite{cakeml-space-cost}.

>>>>

In recent years, aerospace stakeholders have realized that avionics systems are subject to possible cyber-attacks just like other cyber-physical systems.  Thus, in addition to being fault-tolerant, safety-critical avionics systems must also be {\em cyber-resilient}. Cyber-resiliency means that the system is tolerant to cyber-attacks just as safety-critical systems are tolerant to random faults: they recover and continue to execute their mission function, or safely shut down, as requirements dictate.

@@

Another novel aspect of the approach is the synthesis of the AGREE specifications for the high-assurance components to CakeML, a verified compiler implementation for the functional programming language ML \cite{cakeml}. This paper describes in detail the synthesis path from specifications to CakeML code, providing a formal framework in which to argue correctness. CakeML then provides a verified compilation path to several different target binaries proving that the meaning of the CakeML source code is exactly preserved in the final binaries. Assuming that the execution schedule of the deployed cyber-hardened system is as intended by the AADL model, and that the HAMR-generated communication fabric delivers messages between components as expected, the AGREE model checking results hold for the deployed system, \ie, it detects and prevents the indicated cyber-vulnerabilities over all possible finite inputs. Work is ongoing to lift this result to infinite input traces as these systems are inherently reactive and intended to run forever~\cite{case-verified-filter}, \cite{cakeml-space-cost}.

CASE was scoped to address the more common cyber-vulnerabilities that programmers introduce, such as overflow, lack of input validation, supply-chain issues, and identity verification; but not other cyber-vulnerabilities such as side-channel attacks and denial of service.
In this program, we have not invented a new type of filter or monitor in terms of capability, instead our contribution is in the automated synthesis of these components from a formal specification, and a means to show that the synthesis is correct.
